Kyoto VR MQP Paper First Draft

### 2019-08-30 paper.tex
add izi.TRAVEL and images

\begin{abstract}
\end{abstract}

@@

The video game industry has readily embraced augmented reality, leading to the
development of many AR games for smartphones and dedicated head-mounted
displays. Perhaps the most popular AR game, \textit{Pokémon Go}, has been
downloaded over a billion times~\autocite{webster2018}. This game makes use of
GPS and camera data to overlay game objects (in this case fictional monsters) on
top of images of the real world (see Figure
\ref{fig:pokemonGo})~\autocite{concepcion2016}.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{pokemon-go.jpg}
	\caption{A screenshot from the AR game \textit{Pokémon
			Go}~\autocite{vastateparks2016}.}
	\label{fig:pokemonGo}
\end{figure}

@@

@@

@@

\section{Editour: The Tour Editor}
\label{sec:editour}

@@

\subsection{The Need for an Editor}

@@

\subsection{A Complete Tour Definition}
\label{sec:tourDefinition}

@@

\subsection{Editour Backend}
\label{sec:editourBackend}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{turtle-burger.jpg}
	\caption{A rare but delicious turtle burger in the
		wild~\autocite{harvey2002}.}
	\label{fig:turtleBurger}
\end{figure}

@@

>>>>

\begin{abstract}
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{abstract.jpg}
	% Note: you don't actually need the part in square brackets for the caption,
	% but if you omit it the regular caption text will be used for the List of
	% Figures entry.
	\caption[\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock]
	{\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock, National
		Gallery of Art, Washington, D.C.}
	\label{fig:abstract}
\end{figure}
\end{abstract}

@@

The video game industry has readily embraced augmented reality, leading to the
development of many AR games for smartphones and dedicated head-mounted
displays. Perhaps the most popular AR game, \textit{Pokémon Go}, has been
downloaded over a billion times~\autocite{webster2018}. This game makes use of
GPS and camera data to overlay game objects (in this case fictional monsters) on
top of images of the real world~\autocite{concepcion2016} (see Figure
\ref{fig:pokemonGo}).

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{pokemon-go.jpg}
	\caption[A screenshot from the AR game \textit{Pokémon Go}]{A screenshot
		from the AR game \textit{Pokémon Go}~\autocite{vastateparks2016}.}
	\label{fig:pokemonGo}
\end{figure}

@@

To explore existing AR apps for art and culture our group researched and tested
several games, experiences, and platforms related to our project.

@@

Before our project started, Kyoto VR was already using an app with a limited
form of AR for tours. The app, called izi.TRAVEL, allows users to create audio
tours with audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel}, but can be used for tours
of historic sites too.  Kyoto VR used the platform to make an audio tour of
Kinkaku-ji, one of the most popular tourist destinations in
Japan~\autocite{bornoff2000} and an important historic heritage
site~\autocite{unesco}.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{izi-travel.jpg}
	\caption{A screenshot of the izi.TRAVEL app interface}
	\label{fig:iziTravel}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji.jpg}
	\caption[The Golden Pavilion of Kinkaku-ji, Kyoto, Japan]{The Golden
		Pavilion of Kinkaku-ji, Kyoto, Japan~\autocite{davidson2005}}
	\label{fig:kinkakuji}
\end{figure}

By using GPS data from the user's phone to play audio and display images at
specific places in the real world izi.TRAVEL uses a limited form of augmented
reality. Our group aimed to implement and extend this functionality in our own
app. See Section \ref{sec:aruku} for more details.

@@

\subsection{Editour: The Tour Editor}
\label{sec:editour}

@@

\subsubsection{The Need for an Editor}

@@

\subsubsection{A Complete Tour Definition}
\label{sec:tourDefinition}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{editour.jpg}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

\subsubsection{Editour Backend}
\label{sec:editourBackend}

@@

\subsection{ARuku}
\label{sec:aruku}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{turtle-burger.jpg}
	\caption[A rare but delicious turtle burger in the wild]{A rare but
		delicious turtle burger in the wild~\autocite{harvey2002}.}
	\label{fig:turtleBurger}
\end{figure}
